### 2018-05-07 Sections/economics_of_the_quantum_internet.tex
minor

\begin{tabular}{|m{0.21\linewidth}|m{0.22\linewidth}|m{0.155\linewidth}|m{0.155\linewidth}|m{0.2\linewidth}|}

@@

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}}\] & \[\log\left(n \frac{e^{\alpha_\text{sc}n_\text{global}}}{\alpha_\text{sc}n_\text{global}}\right)\]\\

>>>>

\begin{tabular}{|m{0.21\linewidth}|m{0.21\linewidth}|m{0.15\linewidth}|m{0.155\linewidth}|m{0.225\linewidth}|}

@@

	\begin{flushleft}Problem size scaling function (Sec.~\ref{sec:prob_sc_func})\end{flushleft} & \[s = f_\text{size}^{-1}(n\cdot \chi_\text{sc}(n_\text{global}))\] & \[\frac{n}{\alpha_\text{size}}\] & \[n^{\frac{1}{p_\text{size}}} \cdot {n_\text{global}}^\frac{p_\text{sc}-1}{p_\text{size}}\] & \[\alpha_\text{sc}n_\text{global} + \log\left(\frac{n}{\alpha_\text{sc}n_\text{global}}\right)\] \\
